Nilpotent Invariants \\ for Generic Discrete Series of Real Groups

### 2025-12-22 revision_whittaker.tex
Adds [new] and [/new] for clarity

For the action on~(1) see Section~\ref{sec:action_DS}. For the action on~(2) and the equivariance of $\pi \mapsto \Wh(\pi)$, see Section~\ref{sec:action_whitt}. For the action on~(4) and the equivariance of the map $\pi \mapsto \AV(\pi)$, see Section~\ref{sec:action_AV}. For the action on~(3) and the equivariance of $\pi \mapsto \WF(\pi)$ see Section~\ref{sec:action_WF}.

@@

\begin{remarkplain} \textup{The group $Q$ is a finite abelian group, in fact an elementary abelian $2$-group. It is trivial when $G$ is adjoint, and when $G$ is a simple group the cardinal of~$Q$ is at most~$4$. See Remark~\ref{rk:size_Q} for a more precise discussion.} \end{remarkplain}

@@

\begin{remarkplain} \label{rk:size_Q} When $G$ is adjoint, it immediately follows from the definitions that $(G_\ad)^\sigma = (G^\sigma)_{\ad}$, therefore $Q_\sigma(G)$ is trivial in that case.

@@

For the concrete computation of this component group in case  $G$ is simple, see the tables in \cite[Section~10]{galois}. In particular  $Q_\sigma(\R)$ has at most four elements in that case.
\end{remarkplain}

>>>>

\textcolor{red}{[NEW]} For the action on~(1) see Section~\ref{sec:action_DS}. For the action on~(2) and the equivariance of $\pi \mapsto \Wh(\pi)$, see Section~\ref{sec:action_whitt}. For the action on~(4) and the equivariance of the map $\pi \mapsto \AV(\pi)$, see Section~\ref{sec:action_AV}. For the action on~(3) and the equivariance of $\pi \mapsto \WF(\pi)$ see Section~\ref{sec:action_WF}. \textcolor{red}{[/NEW]}

@@

\begin{remarkplain} \textcolor{red}{[NEW]} {The group $Q$ is a finite abelian group, in fact an elementary abelian $2$-group. It is trivial when $G$ is adjoint, and when $G$ is simple  the cardinal of~$Q$ is at most~$4$. See Remark~\ref{rk:size_Q} for a more precise discussion.} \textcolor{red}{[/NEW]}\end{remarkplain}

@@

\begin{remarkplain} \textcolor{red}{(NEW)} \label{rk:size_Q} When $G$ is adjoint, it immediately follows from the definitions that $(G_\ad)^\sigma = (G^\sigma)_{\ad}$, therefore $Q_\sigma(G)$ is trivial in that case.

@@

For the concrete computation of this component group in case  $G$ is simple, see the tables in \cite[Section~10]{galois}. In particular  $Q_\sigma(\R)$ has at most four elements in that case.\textcolor{red}{[/NEW]}
\end{remarkplain}
